Whittaker Models for Real Groups

### 2024-06-14 whittaker.tex
Small tinkering and update to homework

Suppose $\pi$ is a discrete series representation.
Choose a compact Cartan subgroup $T$, and let $\lambda\in\t^*$ be the Harish-Chandra parameter of $\pi$.
Define
\begin{equation} \label{semisimple_orbit_HC} \mathcal{O}_{\pi}=G(\R)\cdot\lambda.\end{equation}

>>>>

Suppose $\pi$ is a discrete series representation. Let $\lambda\in\t^*$ be a representative of the Harish-Chandra parameter of $\pi$.
Define\footnote{AA 2024-VI-14: should perhaps decide if we fix a large chamber from the start and take the HC parameter to live there, or at least be careful about consistency in notation...}
\begin{equation} \label{semisimple_orbit_HC} \mathcal{O}_{\pi}=G(\R)\cdot\lambda.\end{equation}
